Spatiotemporal Data Classification

### 2018-01-13 ProjectReport/BigDataHomework.tex
reorganize folders

	\subsection{Question A}
	The requirement in this part is to preprocess the input training data and create a new file with 3 columns, containingthe trip\_id (a number incrementing by 1 for each trip), the journey\_id(excluding trips with null id) and all points and timestamps in the format: [[timestamp1, longitude1, latitude1], [timestamp2, longitude2, latitude2],...]. The given csv file with the training data was transformed to a dataframe using the relevant pandas library. As already mentioned, the data with null journeyPatternId should be removed from the dataframe, therefore the lines are checked for NaN and "null" journey id. Then, the columns vehicleID and journeyPatternId are groupedby three times in order to create three different dataframes. Foe example, the first dataframe contains the columns: vehicleID, journeyPatternId and timpestamp. In a similar way, the two remaining dataframes were formatted. By concatenating them, the final dataframe contains five columns, where the three last columns contain a list of timestamps, a list of longitudes and a list of latitudes respectively.

@@

	\subsection{Question B}
	The second goal was to clean the given data, based on two criteria: total trip distance should not be less than 2km while max distance between two successive points should not exceed 2km.

@@

	\subsection{Question C}
	This task is implemented in the function visualize\_trips and the created output is stored in the output folder in the gmplots directory. The requirement is to visualize five of the given train trips. For this purporse, the trips list is shuffled in order to visualize random trips and then iterated only for 5 trips. Then, a points list is created having two tuples with all the longitudes and latitudes(function idx\_to\_lonlat in the utils.py).

@@

	\subsection{Question A1}
	For this part a test file is given (test\_set\_a1.csv, included in the input folder) containing additional trips. For each of these trips, the k nearest neighbours are targeted (in this exercise k=5) and an image file is produced, showing all six trips (the test trip and the trips from the training file) on six different maps. Under each map, the test or neighbour index, the journey\_id, the dynamic time warping and the time needed to process the neighbours of this test trip in millisec.

@@

	\subsection{Question A2}
	Following the same logic as above, in the function question\_a2, two dataframes are created for the test and the training dataset using pandas library. The test dataframe is iterated row by row, in order to find the 5 trips from the training dataset which have the longest common subsequence with the specific test trip.

@@

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.50] {question2a1example.jpg}
			\caption{Example of nearest sub-routes trips visualization}
		\end{center}
	\end{figure}

	\subsection{Question B}
	The purpose of this task was to export features for classification for the training dataset. In short, a grid should be created and the points of each trip trace should be replaced by a specific square of the grid. The output file where the exported features are stored is the tripFeatures.csv.

@@

	\subsection{Question C}
	In the method question\_c, a new dataframe is created from the features file, containing the grid cell names. All functions used in this question are in the file JourneyClassification.py. Before starting the classification, the method preprocess\_data was used in order to get the journey\_id of all trips as numbers and also to remove the letter C from the cell names.

>>>>

	\subsection{Data Preprocessing (question A)}
	The requirement in this part is to preprocess the input training data and create a new file with 3 columns, containingthe trip\_id (a number incrementing by 1 for each trip), the journey\_id(excluding trips with null id) and all points and timestamps in the format: [[timestamp1, longitude1, latitude1], [timestamp2, longitude2, latitude2],...]. The given csv file with the training data was transformed to a dataframe using the relevant pandas library. As already mentioned, the data with null journeyPatternId should be removed from the dataframe, therefore the lines are checked for NaN and "null" journey id. Then, the columns vehicleID and journeyPatternId are groupedby three times in order to create three different dataframes. Foe example, the first dataframe contains the columns: vehicleID, journeyPatternId and timpestamp. In a similar way, the two remaining dataframes were formatted. By concatenating them, the final dataframe contains five columns, where the three last columns contain a list of timestamps, a list of longitudes and a list of latitudes respectively.

@@

	\subsection{Clean Data (question B)}
	The second goal was to clean the given data, based on two criteria: total trip distance should not be less than 2km while max distance between two successive points should not exceed 2km.

@@

	\subsection{Trip Visualization (question C)}
	This task is implemented in the function visualize\_trips and the created output is stored in the output folder in the gmplots directory. The requirement is to visualize five of the given train trips. For this purporse, the trips list is shuffled in order to visualize random trips and then iterated only for 5 trips. Then, a points list is created having two tuples with all the longitudes and latitudes(function idx\_to\_lonlat in the utils.py).

@@

	\subsection{Nearest Neighbours (question A1)}
	For this part a test file is given (test\_set\_a1.csv, included in the input folder) containing additional trips. For each of these trips, the k nearest neighbours are targeted (in this exercise k=5) and an image file is produced, showing all six trips (the test trip and the trips from the training file) on six different maps. Under each map, the test or neighbour index, the journey\_id, the dynamic time warping and the time needed to process the neighbours of this test trip in millisec.

@@

	\subsection{Nearest Sub-routes (question A2)}
	Following the same logic as above, in the function question\_a2, two dataframes are created for the test and the training dataset using pandas library. The test dataframe is iterated row by row, in order to find the 5 trips from the training dataset which have the longest common subsequence with the specific test trip.

@@

	\begin{figure} [H]
		\begin{center}
			\includegraphics [scale = 0.50] {question2a2example.jpg}
			\caption{Example of nearest sub-routes trips visualization}
		\end{center}
	\end{figure}

	\subsection{Features extraction (question B)}
	The purpose of this task was to export features for classification for the training dataset. In short, a grid should be created and the points of each trip trace should be replaced by a specific square of the grid. The output file where the exported features are stored is the tripFeatures.csv.

@@

	\subsection{Classification (question C)}
	In the method question\_c, a new dataframe is created from the features file, containing the grid cell names. All functions used in this question are in the file JourneyClassification.py. Before starting the classification, the method preprocess\_data was used in order to get the journey\_id of all trips as numbers and also to remove the letter C from the cell names.
